\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Adjust margins
\usepackage[left=0.3in,top=0.2in,right=0.3in,bottom=0.2in]{geometry}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-12pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Krishna Kumar} \\ \vspace{16pt}
    \href{https://github.com/krishna8421}{\raisebox{-0.2\height}\faGithub\ {github.com/krishna8421}} ~
    \href{https://linkedin.com/in/krishnaaa8421}{\raisebox{-0.2\height}\faLinkedin\ {linkedin.com/in/krishnaaa8421}} ~
    \href{https://krishnaaa.com}{\raisebox{-0.2\height}\faLaptopCode\ {krishnaaa.com}} \\ \vspace{4pt} ~
    \small \raisebox{-0.1\height}\faPhone\ \href{tel:+91860-380-8548}{+91 8603808548} ~ 
    \href{mailto:dev@krishnaaa.com}{\raisebox{-0.2\height}\faEnvelope\ {dev@krishnaaa.com}} 
\end{center}

%-----------SUMMARY-----------
% \section{Summary}
% Tech-savvy and results-driven Computer Science student with a passion for full-stack development and cloud technologies. Proficient in JavaScript, TypeScript, and modern development frameworks. Eager to contribute technical skills and innovation to a dynamic software engineering role at a leading tech company.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{DRDO R\&DE (Engrs)}{Nov '23 -- Mar '24}
{Research Intern}{Pune/Remote}
\resumeItemListStart
\resumeItem{Developed secure peer-to-peer communication protocol using Kyber, a post-quantum cryptography algorithm.}
\resumeItem{Implemented AES-256 encryption for data confidentiality.}
\resumeItem{Contributed to data integrity verification through Dilithium2 signatures.}
\resumeItemListEnd

\resumeSubheading
{ENITIATE}{Jun '23 -- Nov '23}
{Founder's Office Tech Intern}{Remote}
\resumeItemListStart
\resumeItem{Managed team of 5 people, coordinated tasks, and ensured project progress.}
\resumeItem{Optimized GCP development pipeline with GitHub webhooks.}
\resumeItem{Integrated AWS services for secure backend access and implemented CloudFront for efficient data caching.}
\resumeItemListEnd

\resumeSubheading
{SKILLERATE}{Mar '23 -- Apr '23}
{Back-End Developer Intern}{Remote}
\resumeItemListStart
\resumeItem{Developed a critical module for a live Learning Management System (LMS), optimizing user workflow.}
\resumeItem{Collaborated with the Frontend Team to enhance the LMS user interface, improving user experience}
\resumeItem{Led efforts to refine and improve the admin panel, enhancing system manageability.}
\resumeItemListEnd

\resumeSubheading
{MAUKA EDUCATION}{Jul '22 -- Aug '22}
{Back-End Developer Intern}{Remote}
\resumeItemListStart
\resumeItem{Designed secure login/register form and improved spider chart for progress visualization.}
\resumeItem{Enhanced UI responsiveness and upgraded APIs.}
\resumeItemListEnd

\resumeSubheading
{MICROSOFT LEARN STUDENT AMBASSADOR, KIIT CHAPTER}{Jan '22 -- Present}
{Full Stack Developer}{}
\resumeItemListStart
\resumeItem{Organized tech events, hosted workshops, and developed Stocks Dashboard Site.}
\resumeItem{Collaborated with ambassadors to promote 'Tech for All' through events and resources.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Title Generation From Human to Human Conversation} $|$ \emph{PyTorch} $|$ \href{https://github.com/krishna8421/title-generation}{\raisebox{-0.2\height}\faGithub\ }}{Jan '24}
\resumeItemListStart
\resumeItem{Oversaw data preprocessing pipeline for conversational data, ensuring high-quality input.}
\resumeItem{Designed and implemented a PyTorch Seq2Seq model for title generation, contributing to project success.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Kryptic Hunt} $|$ \emph{Next.js, Tailwind, Next Auth} $|$ \href{https://github.com/krishna8421/kryptic-hunt}{\raisebox{-0.2\height}\faGithub\ } \href{https://kryptic-hunt.mlsakiit.com}{\raisebox{-0.2\height}\faLink\ }}{Dec '23}
\resumeItemListStart
\resumeItem{Built a Kryptic hunt game using Next.js, enabling level progression and leaderboard competition.}
\resumeItem{Enhanced user engagement with dynamic level advancement and real-time leaderboard updates.}

\resumeItemListEnd 

\resumeProjectHeading
{\textbf{KTF Backend} $|$ \emph{Express.js, Firebase, TypeScript} $|$ \href{https://github.com/krishna8421/ktf-backend}{\raisebox{-0.2\height}\faGithub\ }}{May '22}
\resumeItemListStart
\resumeItem{Developed a backend for event ticketing, integrating Firebase authentication and Razorpay payments.}
\resumeItem{Implemented Google sign-up, coupon codes, and multiple payment methods.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Public APIs Site} $|$ \emph{Next.js, React.js, Chakra-UI} $|$ \href{https://github.com/krishna8421/public-apis-site}{\raisebox{-0.2\height}\faGithub\ } \href{https://publicapis.krishnaaa.com}{\raisebox{-0.2\height}\faLink\ }}{Jul '21}
\resumeItemListStart
\resumeItem{Developed website for discovering public APIs with a user-friendly interface.}
\resumeItem{Implemented search function by category or keyword.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: JavaScript, TypeScript, Golang, Java} \\
    \textbf{Tools}{: VS Code, AWS, GCP, Figma, Git, Redis, Terraform} \\
    \textbf{Frameworks}{: React, Next.js, Express.js, Gin, PyTorch, Cobra cli} \\
    }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{KALINGA INSTITUTE OF INDUSTRIAL TECHNOLOGY}{2021 -- 2025}
{B. Tech in Computer Science and Engineering, CGPA 7.45/10}{Bhubaneswar, Odisha}
\resumeSubHeadingListEnd

\end{document}
